 % (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com
%
%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{lipsum}
\usepackage{tocloft}
\usepackage{etoolbox}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{etaremune}


\renewcommand{\baselinestretch}{1} 


\robustify\cftdotfill

%-----------------------------------------------------------
%Edit these values as you see fit

\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars


%-----------------------------------------------------------
%Margin setup

\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}


%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{
	\vspace{5pt}
	\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}} \\[-6pt]
	\par\noindent\rule{\textwidth}{0.4pt}
}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
4		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\ressubheadingmod}[2]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & \textit{#2} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

	\begin{center}
		\textbf{\Large Byung-Hak Hwang}	\\[6pt]
		Email address: \href{mailto:byunghakhwang@gmail.com}{byunghakhwang@gmail.com}\\
		% Hompage: \href{}{}\\

	\end{center}

%\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
% &  \\[3pt]
%\end{tabular*}
%\par\noindent\rule{\textwidth}{0.4pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Research interests}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	 
{\vspace{-18pt} \setstretch{1.3}
\begin{itemize}	
\item Algebraic combinatorics, Representation theory.
\end{itemize} }
\vspace{1cm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education and Employment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
  \item\textbf{Research Fellow, Korea Institute for Advanced Study} \\
  May 2024 -- 
  \subitem Mentor: Hyun Kyu Kim

  \item\textbf{Alternative Military Service} \\
  April 2021 -- April 2024

  \item\textbf{Research Fellow, Applied Algebra and Optimization Research Center} \\
  September 2020 -- March 2021
    \subitem Mentor: Jang Soo Kim

	\item\textbf{Ph.D. Mathematics, Seoul National University} \\
  March 2014 -- August 2020
    \subitem Advisor: Woong Kook

  \item\textbf{B.S. Double major in Mathematics, and Electric \& Computer Engineering, Seoul National University} \\
  March 2009 -- February 2014
\end{itemize}

\vspace{1cm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Publications}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\bf Journal publications and preprints}
\begin{etaremune}
    \item \emph{Refined canonical stable Grothendieck polynomials and their duals, Part 2} (with J. Jang, J. S. Kim, M. Song, U-K. Song) \\
    preprint, arXiv:2404.02483, submitted.

    \item \emph{Noncommutative symmetric functions and skewing operators} \\
    preprint, arXiv:2305.08132, submitted.

    \item \emph{Refined canonical stable Grothendieck polynomials and their duals, Part 1} (with J. Jang, J. S. Kim, M. Song, U-K. Song) \\
    Advances in Mathematics, 446:Paper No. 109670, 42, 2024.
    
    \item \emph{Chromatic quasisymmetric functions and noncommutative $P$-symmetric functions} \\
    Transactions of the American Mathematical Society, 377(4):2855–2896, 2024.

    \item \emph{A combinatorial model for the transition matrix between the Specht and $SL_2$-web bases} (with J. Jang and J. Oh) \\
    Forum of Mathematics, Sigma, 11 (2023), E82.
    
    \item \emph{Acyclic orientation polynomials and the sink theorem for chromatic symmetric functions} (with W.-S. Jung, K.-J. Lee, J. Oh, and S.-H. Yu) \\
    Journal of Combinatorial Theory, Series B, 149 (2021), 52-75.

    \item \emph{On linearization coefficients of $q$-Laguerre polynomials} (with J. S. Kim, J. Oh, and S.-H. Yu) \\
    The Electronic Journal of Combinatorics, Volume 27, Issue 2 (2020), P2.22.

    \item \emph{Reverse plane partitions of skew staircase shapes and $q$-Euler numbers} (with J. S. Kim, M. Yoo, and S.-m. Yun) \\
    Journal of Combinatorial Theory, Series A, 168 (2019), 120-163.
\end{etaremune}
	
{\bf Conference proceedings}
\begin{etaremune}
    \item \emph{Refined canonical stable Grothendieck polynomials and their duals} (with J. S. Kim, J. Jang, M. Song, and U-K. Song) \\
    Proceedings of FPSAC 2023.

    \item \emph{Chromatic quasisymmetric functions and noncommutative $P$-symmetric functions} \\ Proceedings of FPSAC 2023.

    \item \emph{A combinatorial model for the transition matrix between the Specht and web bases} (with J. Jang, and J. Oh) \\
    Proceedings of FPSAC 2022.
    
    \item \emph{Acyclic orientation polynomials and the sink theorem for chromatic symmetric functions} (with W.-S. Jung, K.-J. Lee, J. Oh, and S.-H. Yu) \\
    Proceedings of FPSAC 2020.
	
    \item  \emph{On linearization coefficients of $q$-Laguerre polynomials} (with J. S. Kim, J. Oh, and  S.-H. Yu) \\
    Proceedings of FPSAC 2020.
	
    \item \emph{Reverse plane partitions of skew staircase shapes and $q$-Euler numbers} (with J. S. Kim, M. Yoo, and S.-m. Yun) \\
    Proceedings of FPSAC 2018.
\end{etaremune}

% {\bf In preparation}
% \begin{etaremune}
%     \item On $\alpha$-chromatic symmetric functions
% \end{etaremune}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Presentations}
\begin{itemize}
  \item The theory of noncommutative symmetric functions, Topology and Combinatorics seminar at Ajou University, June 2024
  
  \item Logarithmic concavity of Kazhdan--Lusztig \( \widetilde{R} \)-polynomials, Workshop for Young Representation Theorist in Korea, December 2023

  \item Chromatic quasisymmetric functions and noncommutative $P$-symmetric functions, FPSAC 2023, July 2023
  
  \item Chromatic quasisymmetric functions and noncommutative $P$-symmetric functions, Combinatorics on flag varieties and related topics 2023, February 2023
  
  \item A proof of Harada--Precup's conjecture, SKKU Combinatorics seminar, November 2020

  \item Acyclic orientation polynomials, 2020 KMS Annual Meeting, October 2020

  \item Positivity in symmetric functions, AORC Monthly seminar, September 2020
  
  \item Chromatic quasisymmetric functions and noncommutative $P$-symmetric functions, Topology and Combinatorics seminar at Ajou University, September 2020

  \item Acyclic orientation polynomials, 2020 Combinatorics Workshop, August 2020

  \item Acyclic orientation polynomials and the sink theorem for chromatic symmetric functions (poster), The 32nd international conference on Formal Power Series and Algebraic Combinatorics (online), July 2020

  \item Reverse plane partitions of skew staircase shapes and a modification of Lindst\"orm--Gessel--Viennot lemma, The 18th KIAS Combinatorics Workshop, 2017
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \resheading{Organizational experiences}
% \begin{itemize}	

% \item Symmetric Functions in Combinatorics (Online), Aug 23--25, 2022, \href{https://sites.google.com/view/sfc-workshop/home}{https://sites.google.com/view/sfc-workshop/home}

% \item One-day workshop on web bases (Online), Dec 16, 2021

% \end{itemize}


% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \resheading{Awards and Grants}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{itemize}
% \item Best Doctoral Dissertation Awards, College of Natural Sciences, Seoul National University,  2021
% %2,000,000 Korean Won

% \item National Research Foundation of Korea(NRF) grant, 2020--2021
% % 20,000,000 Korean Won

% \item Basic Science Research grant, Seoul National University, 2020
% %6,000,000 Korean won

% \item Outstanding Teaching Assistant Award: Department of Mathematical Science, Seoul National University, 2019

% \item Presidential Science Scholarship: Korea Student Aid Foundation (KOSAF), 2009--2015

% \item Talent Medal of Korea, Presidential award awarded by MyungBak Lee, President of Republic of Korea, 2008

% \end{itemize}



% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \resheading{TA Experience}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{itemize}
% \item Seoul National University, 2015--2020
% \subitem  Calculus I, Spring, 2015, 2016, 2019, 2020
% \subitem  Calculus II, Fall, 2015, 2016, 2019, 2020
% \subitem  Linear algebra, Fall, 2016
% \end{itemize}

\end{document}